### 2019-04-15 paper/paper.tex
small typo fixes

\author{\IEEEauthorblockN{Kevin de Haan, Gregory Neagu, Frederic Sauve-Hoover, Abram Hindle}
  \IEEEauthorblockA{\textit{Department of Computing Science} \\
    \textit{University of Alberta}\\
    Edmonton, Canada\\
  Email: \{kdehaan,neagu,rsauveho,abram.hindle\}@ualberta.ca}
}

@@

As per the original paper we analyzed popularity of \code{npm} packages using three major measures \cite{Wittern:2016}:
\begin{enumerate}
  \item The \textbf{\code{npm} rank} is calculated using the PageRank\cite{brin1998anatomy} of an \code{npm} package within a dependency graph that we built using the
    package metadata as described in Section \ref{PackageMetadata}. PageRank is calculated for every package using a damping factor of 0.85 
    and stopping iterations once the cumulative change in values of vertices went below $10^{-6}$. We then order all packages by their PageRank to determine the
    \code{npm} rank, an relative ranking of package popularity with 1 being the most popular.
  \item The \textbf{download rank} of a package is based on the the gross volume of package downloads from the \code{npm}
    registry, then ordered relatively with 1 being the most downloaded.
  \item \textbf{\code{GitHub} rank} is a measure of the popularity of a package among public \code{GitHub} projects.
    This rank is created from a list of \code{npm} dependency occurrences found in \code{package.json} files, with rank 1
    meaning that the package was the most common dependency among analyzed \code{GitHub} repositories.  
\end{enumerate}

@@

One of the significant benefits of being able to determine
\code{npm} ranks over time is that it allows for the comparison
of similar packages against each other at an objective level.
Figure \ref{selectPackages} shows the npm ranks of selected 
utility packages, as chosen in the original paper \cite{Wittern:2016}.
One of these packages, \code{underscore}, is among the oldest \code{npm} 
utility packages, and the rest have been selected for being
typical alternatives to the \code{underscore} package. Some of these packages,
such as \code{lodash}, are directly or indirectly results of forks from the
\code{underscore} repository. While \code{lodash} has kept up and even surpassed
\code{underscore} in popularity, the majority of newer alternatives are unable
to consistently compete. Calculating ranks for similar groups of packages such as
this allow us to isolate notable, successful packages across the entire span of
the ecosystem's history, as well as evaluate the persistence of the most popular
core packages over time. In the example group of packages presented in Figure \ref{selectPackages},
we can observe that the package established early in the ecosystem's life-cycle
is well-positioned to maintain a significant level of popularity, while the majority of
other packages tend to eventually decline unless they provide something exceptional,
such as \code{lodash} providing API compatibility with \code{underscore}\footnote{https://lodash.com/}.

>>>>

\author{\IEEEauthorblockN{Kevin de Haan, Frederic Sauve-Hoover, Gregory Neagu, Abram Hindle}
  \IEEEauthorblockA{\textit{Department of Computing Science} \\
    \textit{University of Alberta}\\
    Edmonton, Canada\\
  Email: \{kdehaan,rsauveho,neagu,abram.hindle\}@ualberta.ca}
}

@@

As per the original paper we analyzed popularity of \code{npm} packages using three major measures \cite{Wittern:2016}:
\begin{enumerate}
  \item The \textbf{\code{npm} rank} is calculated using the PageRank\cite{brin1998anatomy} of an \code{npm} package within the dependency graph that we built using
    package metadata as described in Section \ref{PackageMetadata}. PageRank is calculated for every package using a damping factor of 0.85,
    and stopping iterations once the cumulative change in values of vertices fell below $10^{-6}$. We then order all packages by their PageRank to determine the
    \code{npm} rank, an relative ranking of package popularity with 1 being the most popular.
  \item The \textbf{download rank} of a package is based on the the gross volume of package downloads from the \code{npm}
    registry, then ordered relatively with 1 being the most downloaded.
  \item \textbf{\code{GitHub} rank} is a measure of the popularity of a package among public \code{GitHub} projects.
    This rank is created from a list of \code{npm} dependency occurrences found in \code{package.json} files, with rank 1
    meaning that the package was the most common dependency among analyzed \code{GitHub} repositories.  
\end{enumerate}

@@

One of the significant benefits of being able to determine
\code{npm} ranks over time is that it allows for the comparison
of similar packages against each other at an objective level.
Figure \ref{selectPackages} shows the npm ranks of selected 
utility packages, as chosen in the original paper \cite{Wittern:2016}.
One of these packages, \code{underscore}, is among the oldest \code{npm} 
utility packages, and the rest have been selected for being
typical alternatives to the \code{underscore} package. Some of these packages,
such as \code{lodash}, are directly or indirectly results of forks from the
\code{underscore} repository. While \code{lodash} has kept up and even surpassed
\code{underscore} in popularity, the majority of newer alternatives are unable
to consistently compete. Calculating ranks for similar groups of packages such as
this allow us to isolate notable, successful packages across the entire span of
the ecosystem's history, as well as evaluate the persistence of the most popular
core packages over time. In the example group of packages presented in Figure \ref{selectPackages},
we can observe that the package established early in the ecosystem's life-cycle
is well-positioned to maintain a significant level of popularity, while the majority of
other packages tend to eventually decline unless they provide something exceptional,
such as \code{lodash}\footnote{https://lodash.com/} providing API compatibility with \code{underscore}\footnote{https://underscorejs.org/}.
